---
title: "wyz.code.offensiveProgramming"
author: "Fabien GELINEAU"
date: "last update on 2019-08-27"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{wyz.code.offensiveProgramming}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

<style>
body {
text-align: justify}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, eval = TRUE, echo = FALSE}
pkn <- 'wyz.code.offensiveProgramming'
```


Package **`r pkn`**  aims to provide a strict type checking inforcement in **R**.

Get access to [Offensive programming book](https://neonira.github.io/offensiveProgrammingBook/) to get introduction and advanced knowledge on the topic. 


# Releases 

Latest release replaces fully olders ones, that are now considered obsoletes. Keep the pace, and  upgrade your packages if you do not use this version or a higher one!

## 1.1.10

Main improvements are 

1. Added many tests to work with RC, S3, S4 and R6 classes
2. enforced higher code coverage (higher than 99.00%)

## 1.1.9

Main improvements are 

1. corrected many typographic errors in i/o with end-user
2. completed unit tests
3. enforced higher code coverage (from 75% up to 99.28%)
4. changed many functions visibility from hidden (internal to package) to visible (end-user available).
5. documentation completion
6. clean up package dependencies. 






